elton trait

### 2019-08-07 data-raw/elton.Rmd
Standardize trait names, remove unecessary columns.

>>>>

Grab only the trait columns we're interested in, standardize column names
```{r}
elton_bird <- elton_bird %>% 
  select(-specid, -ends_with("source"), -ends_with("enteredby"), -ends_with("certainty"), -ends_with("speclevel"), -ends_with("comment"))

elton_mamm <- elton_mamm %>%
  select(-msw3_id, -forstrat_value, -ends_with("source"), -ends_with("certainty"), -ends_with("speclevel"), -ends_with("comment"))
```
